|

### 2023-03-10 paper/03-results.Rmd
TAS template
simplified sub-files; removed headers

---
output: rticles::rss_article
bibliography: bibliography.bib
---

@@

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 7
#| fig.height: 9
source(here("scripts", "01_fig_field.R"))
fig_field
```

>>>>

@@

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "01_fig_field.R"))
fig_field
```
